Stack Safety as a Security Property

### 2020-07-03 main.tex
Rough draft of a section on "enforcement"

>>>>

\section{Enforcement}
\label{sec:enforcement}

\paragraph*{Micropolicies}

\paragraph*{A conservative policy}

This conservative policy enforces our stack safety policy. Moreover, it enforces
a provably stronger \emph{testing property}.

The properties we give are indeed enforceable.

Less conservative policies can be more efficient, but also harder to test.

What is the strongest property enforced by the conservative policy?
%
\rb{Not too much focus on this}

\rb{We have not proved that this policy guarantees our property, but we have
tested it against a stronger property.}

\paragraph*{Testing the conservative policy}

\paragraph*{End-to-end stack safety property}

\paragraph*{Eager vs lazy testing}

\rb{This part should probably be somewhere in the lazy section.}
%
In practice, this \emph{eager policy} is too slow to be of practical interest:
what we really want in practice is a \emph{lazy policy} that can be efficiently
implemented.

We can also test the lazy policy, even if less efficiently, and it should
enforce an inductive property, which may be more amenable to proving.
%
\rb{Would need careful phrasing.}
%
\rb{Implied by the property we started with?}

\rb{Explain and compare what each policy enforces.}
